Bioverse: Potentially Observable Exoplanet Biosignature Patterns Under the UV Threshold Hypothesis for the Origin of Life

### 2025-03-25 src/tex/ms.tex
clarify what is t=0

\subsubsection{Habitable zone occupancy and UV flux}\label{sec:met-hz}
To construct a test \rev{of} the UV~Threshold Hypothesis, we required that life occurs only on planets with sufficient past \gls{UV} irradiation exceeding the origins of life threshold $F_\mathrm{NUV, min}$.
Further, we required this flux to have lasted for a minimum duration $\Delta T_\mathrm{min}$ to allow for a sufficient ``origins timescale''~\citep{Rimmer2023}.
\revv{While there is no consensus on the minimum timescale required for abiogenesis~\citep[e.g.,][]{Lazcano1996}, we adopt  a nominal value of} \rev{$\Delta T_\mathrm{min} = \SI{1}{\mega\year}$.}
\rev{Under $H_1$, longer origins timescales have minimal impact on a generic transit survey but significantly decrease the fraction of inhabited planets around FGK stars, as explored in Appendix~\ref{sec:long-origins}.
}

>>>>

\subsubsection{Habitable zone occupancy and UV flux}\label{sec:met-hz}
To construct a test \rev{of} the UV~Threshold Hypothesis, we required that life occurs only on \revv{\gls{HZ}} planets with sufficient past \gls{UV} irradiation exceeding the origins of life threshold $F_\mathrm{NUV, min}$.
Further, we required this flux to have lasted for a minimum duration $\Delta T_\mathrm{min}$ to allow for a sufficient ``origins timescale''~\citep{Rimmer2023}.
\revv{While there is no consensus on the minimum timescale required for abiogenesis~\citep[e.g.,][]{Lazcano1996}, we adopt  a nominal value of} \rev{$\Delta T_\mathrm{min} = \SI{1}{\mega\year}$.}
\rev{Under $H_1$, longer origins timescales have minimal impact on a generic transit survey but significantly decrease the fraction of inhabited planets around FGK stars, as explored in Appendix~\ref{sec:long-origins}.
}
\revv{
The ``clock'' for the required duration $\Delta T_\mathrm{min}$ starts once the planet resides within the habitable zone and receives NUV flux above the threshold $F_\mathrm{NUV, min}$.
}
